---
title: "Community Needs Assessment"
subtitle: "Service Intake Surveys"
output: html_document
---

<style type="text/css">
.main-container {
  max-width: 90% !important;
  margin: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Load Packages ----
library(here)
library(tidyverse)
library(readxl)
library(janitor)
library(lubridate)
library(scales)
library(patchwork)
library(ggthemes)
library(grid)

# Data ----
# combined surveys
surv <- read_csv("cna_data_all.csv")
# population benchmarks
pops <- read_csv("population_benchmarks.csv")
```

# Contextualizing Community Needs
Below we bring together information about community members seeking services from Network2Work and from the United Way's child care coordinated enrollment system to better understand the scale of community needs.

We also show population-level estimates among a subset of the regional population that aligns with service-seekers. These estimates are derived from the 2019-2023 American Community Survey Public Use Microdata samples for the region.[^1] These population benchmarks provide some context against which to understand the needs of service-seekers and speak to the larger scope of unmet needs within the region.

Because Network2work and United Way's Go2Grow serve different populations, we provide population benchmarks for both.

* Network2Work: The Network2Work intake survey includes 441 job-seekers who enrolled in the program between July 1, 2022 and June 30, 2024 from the region (see below). By definition, these community members are seeking employment. The earned annual wages among those seeking services ranged between \$0 and \$70,000, with a median value of \$15,700.[^2] Respondents to this survey are individuals.
  + Population benchmark: The population benchmark data includes person-level data for individuals between the ages of 18 to 65 who are in the labor force (though not necessarily currently employed) with wages below $75,000.[^3]

* United Way: The United Way's coordinated enrollment intake survey includes 1,442 child-care seekers who enrolled between July 1, 2023 and June 30, 2024 from the region (see below). By definition, these community members have at least one child under 6 at home. The family income among those seeking services ranged between \$0 and \$160,000, with a median value of \$34,700.[^4] Respondents to this survey represent family households.
  + Population benchmark: The population benchmark data includes family-level data for families with at least one child under 6 and with family incomes below $160,000.[^5]

## Who are service seekers?

### Locality {.tabset}

Both Network2Work and United Way's Go2Grow serve residents beyond the localities shown here. However, the intake data was restricted to residents of Albemarle, Charlottesville, Fluvanna, Greene, Louisa, and Nelson.

#### Combined
```{r loc3, fig.width = 20}
locality <- surv %>% filter(survey_question == "Locality")
title <- locality$survey_question[1]

p1 <- locality %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- locality %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%") )) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### Network2Work
```{r loc1, fig.width = 20}
locality <- surv %>% 
  filter(survey_question == "Locality", survey == "Network2Work")
title <- locality$survey_question[1]

p1 <- locality %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Job-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

locality_pops <- pops %>% 
  filter(pop_equiv == "Network2Work", question_equiv == "Locality") %>% 
  mutate(group = str_extract(group, "(\\w+)"))

p2 <- locality_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### United Way
```{r loc2, fig.width = 20}
locality <- surv %>% 
  filter(survey_question == "Locality", survey == "United Way")
title <- locality$survey_question[1]

p1 <- locality %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[3]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Child-Care-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

locality_pops <- pops %>% 
  filter(pop_equiv == "United Way", question_equiv == "Locality") %>% 
  mutate(group = str_extract(group, "(\\w+)"))

p2 <- locality_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title," Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```


### Age {.tabset}

#### Combined
```{r age3, fig.width = 20}
age <- surv %>% filter(survey_question == "Age")
title <- age$survey_question[1]

p1 <- age %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- age %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%") )) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### Network2Work
```{r age1, fig.width = 20}
age <- surv %>% 
  filter(survey_question == "Age", survey == "Network2Work")
title <- age$survey_question[1]

p1 <- age %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Job-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

age_pops <- pops %>% 
  filter(pop_equiv == "Network2Work", question_equiv == "Age") 

p2 <- age_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### United Way
```{r age2, fig.width = 20}
age <- surv %>% 
  filter(survey_question == "Age", survey == "United Way")
title <- age$survey_question[1]

p1 <- age %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[3]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Child-Care-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

age_pops <- pops %>% 
  filter(pop_equiv == "United Way", question_equiv == "Age") 

p2 <- age_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```


### Sex {.tabset}

#### Combined
```{r sex3, fig.width = 20}
sex <- surv %>% filter(survey_question == "Gender")
title <- sex$survey_question[1]

p1 <- sex %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- sex %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%") )) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### Network2Work
```{r sex1, fig.width = 20}
sex <- surv %>% 
  filter(survey_question == "Gender", survey == "Network2Work")
title <- sex$survey_question[1]

p1 <- sex %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Job-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

sex_pops <- pops %>% 
  filter(pop_equiv == "Network2Work", question_equiv == "Sex") 

p2 <- sex_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = "Sex Population Benchmark") +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### United Way
```{r sex2, fig.width = 20}
sex <- surv %>% 
  filter(survey_question == "Gender", survey == "United Way")
title <- sex$survey_question[1]

p1 <- sex %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[3]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Child-Care-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

sex_pops <- pops %>% 
  filter(pop_equiv == "United Way", question_equiv == "Sex") 

p2 <- sex_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = "Sex Population Benchmark") +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

### Race {.tabset}

#### Combined
```{r race3, fig.width = 20}
race <- surv %>% filter(survey_question == "Race")
title <- race$survey_question[1]

p1 <- race %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- race %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%") )) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### Network2Work
```{r race1, fig.width = 20}
race <- surv %>% 
  filter(survey_question == "Race", survey == "Network2Work")
title <- race$survey_question[1]

p1 <- race %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Job-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

race_pops <- pops %>% 
  filter(pop_equiv == "Network2Work", question_equiv == "Race") 

p2 <- race_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### United Way
```{r race2, fig.width = 20}
race <- surv %>% 
  filter(survey_question == "Race", survey == "United Way")
title <- race$survey_question[1]

p1 <- race %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[3]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Child-Care-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

race_pops <- pops %>% 
  filter(pop_equiv == "United Way", question_equiv == "Race") 

p2 <- race_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

### Ethnicity {.tabset}

#### Combined
```{r ethn3, fig.width = 20}
ethn <- surv %>% filter(survey_question == "Ethnicity")
title <- ethn$survey_question[1]

p1 <- ethn %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- ethn %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%") )) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### Network2Work
```{r ethn1, fig.width = 20}
ethn <- surv %>% 
  filter(survey_question == "Ethnicity", survey == "Network2Work")
title <- ethn$survey_question[1]

p1 <- ethn %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Job-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

ethn_pops <- pops %>% 
  filter(pop_equiv == "Network2Work", question_equiv == "Ethnicity") 

p2 <- ethn_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### United Way
```{r ethn2, fig.width = 20}
ethn <- surv %>% 
  filter(survey_question == "Ethnicity", survey == "United Way")
title <- ethn$survey_question[1]

p1 <- ethn %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[3]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Child-Care-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

ethn_pops <- pops %>% 
  filter(pop_equiv == "United Way", question_equiv == "Ethnicity") 

p2 <- ethn_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```


## Resources and Challenges

### Education {.tabset}
#### Combined
```{r educ3, fig.width = 20}
educ <- surv %>% filter(survey_question == "Education Level") %>% 
  mutate(data_point = factor(data_point, 
                             levels = c("Did Not Complete High School", "GED", "High School Graduate", "Some College or Advanced Training", "Associate's Degree", "Bachelor's Degree", "Graduate Degree")))
title <- educ$survey_question[1]

p1 <- educ %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- educ %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%") )) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### Network2Work
```{r educ1, fig.width = 20}
educ <- surv %>% 
  filter(survey_question == "Education Level", survey == "Network2Work") %>% 
  mutate(data_point = factor(data_point, 
                             levels = c("Did Not Complete High School", "GED", "High School Graduate", "Some College or Advanced Training", "Associate's Degree", "Bachelor's Degree", "Graduate Degree")))
title <- educ$survey_question[1]

p1 <- educ %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Job-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

educ_pops <- pops %>% 
  filter(pop_equiv == "Network2Work", question_equiv == "Education Level")  %>% 
  mutate(group = factor(group, 
                             levels = c("Did Not Complete High School", "GED", "High School Graduate", "Some College or Advanced Training", "Associate's Degree", "Bachelor's Degree", "Graduate Degree")))

p2 <- educ_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### United Way
```{r educ2, fig.width = 20}
educ <- surv %>% 
  filter(survey_question == "Education Level", survey == "United Way")%>% 
  mutate(data_point = factor(data_point, 
                             levels = c("Did Not Complete High School", "GED", "High School Graduate", "Some College or Advanced Training", "Associate's Degree", "Bachelor's Degree", "Graduate Degree")))
title <- educ$survey_question[1]

p1 <- educ %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[3]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Child-Care-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

educ_pops <- pops %>% 
  filter(pop_equiv == "United Way", question_equiv == "Education Level") %>% 
  mutate(group = factor(group, 
                             levels = c("Did Not Complete High School", "GED", "High School Graduate", "Some College or Advanced Training", "Associate's Degree", "Bachelor's Degree", "Graduate Degree")))

p2 <- educ_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

### Disability {.tabset}

#### Combined
```{r dis3, fig.width = 20}
dis <- surv %>% filter(str_detect(survey_question, "Disability"))
title <- dis$survey_question[1]

p1 <- dis %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- dis %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%") )) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### Network2Work
```{r dis1, fig.width = 20}
dis <- surv %>% filter(str_detect(survey_question, "Disability") &
                         survey == "Network2Work")
title <- dis$survey_question[1]

p1 <- dis %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Job-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

dis_pops <- pops %>% 
  filter(pop_equiv == "Network2Work", question_equiv == "Disability") 

p2 <- dis_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = "Disability Population Benchmark") +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### United Way
```{r dis2, fig.width = 20}
dis <- surv %>% 
  filter(str_detect(survey_question, "Disability"), 
         survey == "United Way")
title <- dis$survey_question[1]

p1 <- dis %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[3]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Child-Care-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

dis_pops <- pops %>% 
  filter(pop_equiv == "United Way", question_equiv == "Disability") 

p2 <- dis_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = "Disability Population Benchmark") +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

### Military service {.tabset}

#### Combined
```{r mil3, fig.width = 20}
mil <- surv %>% filter(survey_question == "Military Service")
title <- mil$survey_question[1]

p1 <- mil %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- mil %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%") )) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### Network2Work
```{r mil1, fig.width = 20}
mil <- surv %>% 
  filter(survey_question == "Military Service", survey == "Network2Work")
title <- mil$survey_question[1]

p1 <- mil %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Job-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

mil_pops <- pops %>% 
  filter(pop_equiv == "Network2Work", question_equiv == "Military Service") 

p2 <- mil_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### United Way
```{r mil2, fig.width = 20}
mil <- surv %>% 
  filter(survey_question == "Military Service", survey == "United Way")
title <- mil$survey_question[1]

p1 <- mil %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[3]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Child-Care-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

mil_pops <- pops %>% 
  filter(pop_equiv == "United Way", question_equiv == "Military Service") 

p2 <- mil_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

### System-Impacted

There is no local benchmark data on the number or percent of residents who have been impacted by carcereal systems.

#### Combined
```{r inc3, fig.width = 20}
inc <- surv %>% filter(str_detect(survey_question, "Incarceration history"))
title <- inc$survey_question[1]

p1 <- inc %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- inc %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%") )) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

### Language {.tabset}

Only the United Way intake survey includes any notable number of residents who primarily speak a language other than English at home.

#### Combined
```{r lang3, fig.width = 20}
lang <- surv %>% filter(str_detect(survey_question, "Primary Language"))
title <- lang$survey_question[1]

p1 <- lang %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8,
           fill = few_pal(palette = "Medium")(3)[[3]]) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- lang %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%"))) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8, 
           fill = few_pal(palette = "Medium")(3)[[3]]) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### Network2Work
```{r lang1, fig.width = 20}
lang_pops <- pops %>% 
  filter(pop_equiv == "Network2Work", question_equiv == "Primary Language") 

p2 <- lang_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

grob <- textGrob('Only 5 of 441 seekers (1.1%)\n
               reported needing assistance understanding\n
               and interpreting English.',
               gp = gpar(col = few_pal(palette = "Medium")(3)[[2]], fontsize = 25))

wrap_elements(grob) + wrap_elements(p2)
```

#### United Way
```{r lang2, fig.width = 20}
lang <- surv %>% 
  filter(survey_question == "Primary Language", survey == "United Way")
title <- lang$survey_question[1]

p1 <- lang %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[3]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Child-Care-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

lang_pops <- pops %>% 
  filter(pop_equiv == "United Way", question_equiv == "Primary Language") 

p2 <- lang_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

## Family

### Children at Home {.tabset}

By definition, child-care seekers have young children at home.

#### Combined
```{r child3, fig.width = 20}
child <- surv %>% filter(str_detect(survey_question, "children"))
title <- child$survey_question[1]

p1 <- child %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- child %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%") )) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### Network2Work
```{r child1, fig.width = 20}
child <- surv %>% 
  filter(str_detect(survey_question, "children"), survey == "Network2Work")
title <- child$survey_question[1]

p1 <- child %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Job-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

child_pops <- pops %>% 
  filter(pop_equiv == "Network2Work", question_equiv == "Children at Home") 

p2 <- child_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### United Way
```{r child2, fig.width = 20}
child <- surv %>% 
  filter(str_detect(survey_question, "children"), survey == "United Way")
title <- child$survey_question[1]

p1 <- child %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[3]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Child-Care-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

child_pops <- pops %>% 
  filter(pop_equiv == "United Way", question_equiv == "Children at Home") 

p2 <- child_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

The population benchmark was defined as families with a child under the age of 6 living at home.

### Childcare Needs

By definition, the United Way child-care seekers all need support finding and affording child care. Only responses from Network2Work job-seekers are shown here. There is no local comparable population benchmark available.

#### Combined
```{r care3, fig.width = 20}
care <- surv %>% filter(str_detect(survey_question, "Childcare"))
title <- care$survey_question[1]

p1 <- care %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8,
           fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- care %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%") )) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8,
           fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

### Single Parenting {.tabset}

#### Combined
```{r parent3, fig.width = 20}
parent <- surv %>% filter(survey_question == "Single Parent")
title <- parent$survey_question[1]

p1 <- parent %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- parent %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%") )) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### Network2Work
```{r parent1, fig.width = 20}
parent <- surv %>% 
  filter(survey_question == "Single Parent", survey == "Network2Work")
title <- parent$survey_question[1]

p1 <- parent %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Job-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

parent_pops <- pops %>% 
  filter(pop_equiv == "Network2Work", question_equiv == "Single Parent") 

p2 <- parent_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### United Way
```{r parent2, fig.width = 20}
parent <- surv %>% 
  filter(survey_question == "Single Parent", survey == "United Way")
title <- parent$survey_question[1]

p1 <- parent %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[3]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Child-Care-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

parent_pops <- pops %>% 
  filter(pop_equiv == "United Way", question_equiv == "Single Parent") 

p2 <- parent_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```


## Employment and Benefits

### Employment {.tabset}

#### Combined
```{r emp3, fig.width = 20}
emp <- surv %>% filter(str_detect(survey_question, "Employment"))
title <- emp$survey_question[1]

p1 <- emp %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- emp %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%") )) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### Network2Work
```{r emp1, fig.width = 20}
emp <- surv %>% 
  filter(str_detect(survey_question, "Employment"), survey == "Network2Work")
title <- emp$survey_question[1]

p1 <- emp %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Job-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

emp_pops <- pops %>% 
  filter(pop_equiv == "Network2Work", question_equiv == "Employment Status") 

p2 <- emp_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### United Way
```{r emp2, fig.width = 20}
emp <- surv %>% 
  filter(str_detect(survey_question, "Employment"), survey == "United Way")
title <- emp$survey_question[1]

p1 <- emp %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[3]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Child-Care-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

emp_pops <- pops %>% 
  filter(pop_equiv == "United Way", question_equiv == "Employment Status") 

p2 <- emp_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

### Receiving SNAP Benefits {.tabset}

#### Combined
```{r snap3, fig.width = 20}
snap <- surv %>% filter(str_detect(survey_question, "SNAP"))
title <- snap$survey_question[1]

p1 <- snap %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- snap %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%") )) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### Network2Work
```{r snap1, fig.width = 20}
snap <- surv %>% 
  filter(str_detect(survey_question, "SNAP"), survey == "Network2Work")
title <- snap$survey_question[1]

p1 <- snap %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Job-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

snap_pops <- pops %>% 
  filter(pop_equiv == "Network2Work", str_detect(question_equiv, "SNAP")) 

p2 <- snap_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### United Way
```{r snap2, fig.width = 20}
snap <- surv %>% 
  filter(str_detect(survey_question, "SNAP"), survey == "United Way")
title <- snap$survey_question[1]

p1 <- snap %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[3]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Child-Care-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

snap_pops <- pops %>% 
  filter(pop_equiv == "United Way", str_detect(question_equiv, "SNAP")) 

p2 <- snap_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```


### Income {.tabset}

Income data from United Way's child-care seekers was inconsistently available. Thus, it is not used here.

#### Combined
```{r wage3, fig.width = 20}
wage <- surv %>% filter(str_detect(survey_question, "Wages")) %>% 
  mutate(data_point = factor(data_point),
         data_point = fct_shift(data_point, -1))
title <- wage$survey_question[1]

p1 <- wage %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8,
           fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- wage %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%") )) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8,
           fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### Network2Work
```{r wage1, fig.width = 20}
wage <- surv %>% filter(str_detect(survey_question, "Wages")) %>% 
  mutate(data_point = factor(data_point),
         data_point = fct_shift(data_point, -1))
title <- wage$survey_question[1]

p1 <- wage %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Job-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

wage_pops <- pops %>% 
  filter(pop_equiv == "Network2Work", str_detect(question_equiv, "Wages")) %>% 
    mutate(group = factor(group),
         group = fct_shift(group, -1))


p2 <- wage_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```


## Housing and Transportation

### Housing Instability {.tabset}

Job seekers with unstable housing indicated that they either needed to find another place to live in the next 14 days, 1 month, or 3 months or that they neither rent nor own their current residence but instead jump from couch to couch, live in a hotel, are staying in an emergency shelter, or live in a place not meant for housing (e.g., a car).

Child-care seekers with unstable housing indicated that they are currently living in temporary or transitional housing, are currently experiencing homelessness, or live in a campground, motel, or shelter. Additionally, child-care seekers who did not report currently unstable housing but indicated having moved at least twice in more than one year or more than twice in three years are identified as experiencing prior instability or frequent movement.

#### Combined
```{r house3, fig.width = 20}
house <- surv %>% filter(str_detect(survey_question, "Housing")) %>% 
  mutate(data_point = factor(data_point, 
                             levels = c("Stable", "Unstable", "Prior instability and/or frequent movement")))
title <- house$survey_question[1]

p1 <- house %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- house %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%") )) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

#### Network2Work
```{r house1, fig.width = 20}
house <- surv %>% filter(survey == "Network2Work" & str_detect(survey_question, "Housing")) 
title <- house$survey_question[1]

p1 <- house %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Job-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

house_pops <- pops %>% 
  filter(pop_equiv == "Network2Work", str_detect(question_equiv, "Housing")) %>% 
  mutate(group = factor(group, 
                        levels = c("Not Burdened", "Burdened", "Severely Burdened",
                                   "Not Overcrowded", "Overcrowded",
                                   "No Move within Year", "Moved within Year")))

p2 <- house_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

Approximately identical measures are not available in the population benchmark data. Instead, related measures are shown: the percent who have moved within the last year, or not moved; the percent who's households are overcrowded (with more than two people per bedroom or more than one person per rooms overall), or not overcrowded; and the percent who are severely housing burdened (pay more than 50% of income on shelter), housing burdened (pay between 30% and 50% of income on shelter), and not housing burdened.

#### United Way
```{r house2, fig.width = 20}
house <- surv %>% filter(survey == "United Way" & str_detect(survey_question, "Housing")) %>% 
  mutate(data_point = factor(data_point, 
                             levels = c("Stable", "Unstable", "Prior instability and/or frequent movement")))
title <- house$survey_question[1]

p1 <- house %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[3]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Child-Care-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

house_pops <- pops %>% 
  filter(pop_equiv == "United Way", str_detect(question_equiv, "Housing")) %>% 
  mutate(group = factor(group, 
                        levels = c("Not Burdened", "Burdened", "Severely Burdened",
                                   "Not Overcrowded", "Overcrowded",
                                   "No Move within Year", "Moved within Year")))

p2 <- house_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

Approximately identical measures are not available in the population benchmark data. Instead, related measures are shown: the percent who have moved within the last year, or not moved; the percent who's households are overcrowded (with more than two people per bedroom or more than one person per rooms overall), or not overcrowded; and the percent who are severely housing burdened (pay more than 50% of income on shelter), housing burdened (pay between 30% and 50% of income on shelter), and not housing burdened.


### Transportation needs {.tabset}

Job seekers who indicated that they need help getting to work, plan to walk, or whose ride may be unreliable are identified as not having reliable transportation; those who indicated they have car access but the car would not pass inspection or was not registered are identified as having car access that isn't reliable or registered; those who indicated having a very reliable ride, having reliable car access with up-to-date inspections and registrations, or who plan to take the bus are identified as not having transportation needs.

Only child-care seekers who answered they did not have reliable transportation are identified as not having reliable transportation. Child-care seekers were also asked if transportation or working hours posed barriers in getting their child to school.

#### Combined
```{r tran3, fig.width = 20}
tran <- surv %>% filter(str_detect(survey_question, "Transportation")) %>% 
  mutate(data_point = factor(data_point, 
                             levels = c("None", "Does not have reliable transportation", "Have car access, not reliable or registered", "Does not have drivers license", "Transportation is a barrier to getting child to and from school", "Works longer hours than school day")))
title <- tran$survey_question[1]

p1 <- tran %>% 
  ggplot(aes(x = data_point, y = survey_count, fill = survey, label = survey_count)) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                     name = "Number of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Count")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 13),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p2 <- tran %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), fill = survey, label = paste0(round(survey_percent, 0), "%") )) +  
  geom_bar(stat = "identity", position = position_dodge2(width = 0.9, preserve = "single"), width = 0.8) +
  geom_text(position = position_dodge2(width = 0.9, preserve = "single"), 
            vjust = -0.5,
            size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Responses") +
  scale_fill_few() +
  labs(title = paste0(title, " Percent")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```


#### Network2Work
```{r tran1, fig.width = 20}
tran <- surv %>% filter(survey == "Network2Work" & str_detect(survey_question, "Transportation")) %>% 
  mutate(data_point = factor(data_point, 
                             levels = c("None", "Does not have reliable transportation", "Have car access, not reliable or registered", "Does not have drivers license")))
title <- tran$survey_question[1]

p1 <- tran %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[2]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Job-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

tran_pops <- pops %>% 
  filter(pop_equiv == "Network2Work", str_detect(question_equiv, "Transportation"), group != "Commute by Car") %>% 
  mutate(group = factor(group, 
                        levels = c("Household has Car", "Household has no Car", "Commute by Car: Own Car", "Commute by Car: Carpool", "Commute by Motorcycle, Bike, Walk, Other", "Commute by Public Transportation")))

p2 <- tran_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

Approximately identical measures are not available in the population benchmark data. Instead, related measures are shown: the percent of households with access to at least one car, or not; the percent of workers who commute to work in their own car, in a carpool, by public transportation, or by other means.

#### United Way
```{r tran2, fig.width = 20}
tran <- surv %>% filter(survey == "United Way" & str_detect(survey_question, "Transportation")) %>% 
  mutate(data_point = factor(data_point, 
                             levels = c("None", "Does not have reliable transportation", "Does not have drivers license", "Transportation is a barrier to getting child to and from school", "Works longer hours than school day")))
title <- tran$survey_question[1]

p1 <- tran %>% 
  ggplot(aes(x = data_point, y = round(survey_percent, 0), label = paste0(round(survey_percent, 0), "%") )) +  
  geom_col(fill = few_pal(palette = "Medium")(3)[[3]]) +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Child-Care-Seekers") +
  labs(title = paste0(title, " Seekers")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

tran_pops <- pops %>% 
  filter(pop_equiv == "United Way", str_detect(question_equiv, "Transportation")) %>% 
  mutate(group = factor(group, 
                        levels = c("Household has Car", "Household has no Car", "Commute by Car: Own Car", "Commute by Car: Carpool", "Commute by Motorcycle, Bike, Walk, Other", "Commute by Public Transportation")))

p2 <- tran_pops %>% 
  ggplot(aes(x = group, y = round(percent, 0), label = paste0(round(percent, 0), "%") )) +  
  geom_col() +
  geom_text(vjust = -0.5, size = 4.5) +
  scale_x_discrete(labels = scales::label_wrap(10),
                   name = "") +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0, 0.08)),
                     name = "% of Benchmark Population") +
  labs(title = paste0(title, " Population Benchmark")) +
  coord_cartesian(expand=FALSE, clip="off") +
  theme_minimal() +
  theme(legend.position = "top",
        legend.justification.top = "left",
        legend.title=element_blank(),
        legend.text = element_text(size = 14),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(color = "black", size = 13),
        axis.ticks = element_blank(),
        plot.title.position= "plot",
        plot.caption.position = "plot",
        text = element_text(size = 13),
        plot.title = element_text(size = 18, margin=margin(0,0,30,0)),         
        plot.subtitle = element_text(size = 18),
        plot.caption = element_text(size = 12))

p1 + p2
```

Approximately identical measures are not available in the population benchmark data. Instead, related measures are shown: the percent of households with access to at least one car, or not; the percent of workers who commute to work in their own car, in a carpool, by public transportation, or by other means.


[^1]: The Public Use Microdata Areas for the greater Charlottesville region include respondents from Albemarle, Charlottesville, Fluvanna, Greene, Louisa, and Nelson.
[^2]: The wage range is based on the 99th percentile value to minimize outliers.
[^3]: The benchmark population based on these criteria make up 36% of the regional population.
[^4]: The family income range is based on the 97.5th percentile value to minimize outliers.
[^5]: The benchmark population based on these criteria make up 6% of the regional households.
