---
title: "Community Needs Assessment: Income, Poverty"
output: html_document
date: "2024-09-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(leaflet)
library(viridis)

load("poverty.RData")
load("income.RData")
```

## Income {.tabset}

The figure below shows the distribution of income -- the percent of the population or of families within each income range -- by county.

### Percent of People

```{r inc1}
ggplot(income_county) +
  geom_col(aes(x = fct_rev(income_bin), y = percent, fill = income_bin)) +
  scale_fill_viridis_d(direction = -1) +
  guides(fill = FALSE) + 
  coord_flip() +
  facet_wrap(~NAME) +
  labs(x = "", y = "Percent of Population", 
       title = "Population (%) by Income Range")
```

### Percent of Families

```{r inc2}
ggplot(fam_income_county) +
  geom_col(aes(x = fct_rev(income_bin), y = percent, fill = income_bin)) +
  scale_fill_viridis_d(direction = -1) +
  guides(fill = FALSE) + 
  coord_flip() +
  facet_wrap(~NAME) +
  labs(x = "", y = "Percent of Families", 
       title = "Families (%) by Income Range")
```

## Poverty {.tabset}

The maps below show the percent of people and families in poverty by county, census tract, and block group for the six localities in the health district/planning district.

### Localities

```{r cnty}
pal <- colorBin(viridis_pal(option = "C")(10), domain = pov_blkgp_sf$percent)

leaflet() %>% 
  leaflet(width = "100%") %>%
  addProviderTiles("CartoDB.Positron") %>% 
  addPolygons(data = pov_county_sf,
              fillColor = ~pal(percent),
              weight = 1,
              opacity = 1,
              color = "white", 
              fillOpacity = 0.6,
              smoothFactor = 0.3,
              highlight = highlightOptions(
                weight = 1, fillOpacity = 0.8, bringToFront = T),
              popup = paste0("Percent below Poverty: ", pov_county_sf$percent, "%", "<br>",
                             "County: ", pov_county_sf$name)) %>% 
  addLegend("bottomright", pal = pal, values = pov_county_sf$percent, 
            title = "Percent below Poverty", opacity = 0.7)
```

### Census Tracts

```{r tract}
leaflet() %>% 
  leaflet(width = "100%") %>%
  addProviderTiles("CartoDB.Positron") %>% 
  addPolygons(data = pov_tract_sf,
              fillColor = ~pal(percent),
              weight = 1,
              opacity = 1,
              color = "white", 
              fillOpacity = 0.6,
              smoothFactor = 0.3,
              highlight = highlightOptions(
                weight = 1, fillOpacity = 0.8, bringToFront = T),
              popup = paste0("Percent below Poverty: ", pov_tract_sf$percent, "%", "<br>",
                             "Name of Area: ", pov_tract_sf$tractnames, "<br>",
                             "Census Tract: ", pov_tract_sf$GEOID)) %>% 
  addLegend("bottomright", pal = pal, values = pov_tract_sf$percent, 
            title = "Percent below Poverty", opacity = 0.7)
```

### Census Block Groups 

```{r blkgp}
leaflet() %>% 
  leaflet(width = "100%") %>%
  addProviderTiles("CartoDB.Positron") %>% 
  addPolygons(data = pov_blkgp_sf,
              fillColor = ~pal(percent),
              weight = 1,
              opacity = 1,
              color = "white", 
              fillOpacity = 0.6,
              smoothFactor = 0.3,
              highlight = highlightOptions(
                weight = 1, fillOpacity = 0.8, bringToFront = T),
              popup = paste0("Percent below Poverty: ", pov_blkgp_sf$percent, "%", "<br>",
                             "Census Block Group: ", pov_blkgp_sf$GEOID)) %>% 
  addLegend("bottomright", pal = pal, values = pov_blkgp_sf$percent, 
            title = "Percent below Poverty", opacity = 0.7)

```





